---
output: rmarkdown::github_document
---

# pubcrawl

Convert 'epub' Files to Text

## Description

Convert 'epub' Files to Text

The 'epub' file format is really just a structured 'ZIP' archive with 
metadata, graphics and (usually) 'HTML' text. Tools are provided to turn an 'epub'
file into a tidy data frame.

## What's Inside The Tin

The following functions are implemented:

- `epub_to_text`:	Convert an epub file into a data frame of plaintext chapters

## NOTE

There are edge cases I've totally not covered yet. Feel free to jump in and make this a real, useful package!

## TODO

- [ ] Refactor so there aren't so many heavy dependencies
- [ ] Try to get `hgr` on CRAN so it's not a GH dep
- [ ] Better docs
- [ ] Embed some epubs for examples and tests
- [ ] Setup Travis, Appveyor, code coverage

## Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/pubcrawl")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

## Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(pubcrawl)
library(tidyverse)

# current verison
packageVersion("pubcrawl")

```

```{r}
epub_to_text("~/Data/R Packages.epub")
```
